On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-27 Manuscript/manuscript.tex
Responded to Some Comments

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let \jy{No need to number an equation if it is not referred to}
\begin{equation*}
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\end{equation*}
Define
\begin{equation*}
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\end{equation*}
and
\begin{equation*}
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\end{equation*}
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

@@

\jy{I like the font size of the labels and axis of Figure 4. They are still
  overly large in Figures 1--3. The panel head is also too wide. The axis ticks
  look crowded. The panel
  labels on the right also does not look pretty. I'd prefer the old version if
  the font sizes were smaller.}

@@

\jy{Is textbf of Figure requried? Never manual formatting.}
For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
that all methods eventually approach correct coverage of $\mu$ as sample size 
increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
correct coverage, except for samples with strong negative dependence, in which 
case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
nominal level for all combinations of $n$ and $\phi$. All methods seem to 
require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
negative dependence versus positive dependence. For example, BC CIs recover 
$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
stronger, holding everything else equal, coverage increases, which lead to the 
Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
stronger, holding everything else equal, coverage decreases, and a larger sample 
is necessary to recover~$\mu$.

@@

To calibrate the copula parameters, we first constructed a multivariate
exponential distribution from a normal copula using the \textsl{copula} package.
\citep{copula} Then we computed $E[XY]$, which 
requires double integration using the \textsl{pracma} package. \citep{pracma} 
Finally, we obtained true $\rho = E[XY] - 1$, which was used as the target
parameter when evaluating CI performance when estimating $\rho$.
After this step, we again plotted empirical coverage 
rates for $\mu$, $\sigma$, and $\rho$, as well as 95\% confidence intervals of 
the real coverage. These are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_rho}}.

@@

\jy{cite the copula book instead of the package}

\jy{comment on the similarity of the results with those reported in the main text.}

@@

Although there are differences in the ranges of sample sizes needed to cover 
parameters of a normally distributed AR(1) process versus an exponentially 
distributed AR(1) process, the trends and patterns are generally the same.
Student's $t$ CIs still appear to yield higher coverage rates than other 
methods. Performance is still generally better when temporal dependence is 
negative rather than positive. Most importantly, percentile, BC, and BCA CIs
still deteriorate in coverage of $\rho$ as sample size increases. As exhibited 
in Figure~\ref{fig:eri}, percentile and BC CIs still have the same bias
issue.

>>>>

\paragraph{Bias-Corrected and Accelerated (BCA) CI}
The BCA CI was first suggested in \citet{efron1987better}. Let $Z_{(i)}$ be the 
original sample without the $i$th block $z_i$ for $i \in \{1, \ldots, k\}$, let 
$\hat{\theta}_{(i)}$ be the statistic of $Z_{(i)}$, and let 
$\hat{\theta}_{(.)} = k^{-1}\sum_{i=1}^{k} \hat{\theta}_{(i)}$. 
Let \jy{No need to number an equation if it is not referred to}
\mc{addressed}
\begin{equation*}
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\end{equation*}
Define
\begin{equation*}
\alpha_1 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{\alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{\alpha/2})}\right)
\end{equation*}
and
\begin{equation*}
\alpha_2 = \Phi\left(\hat{z}_{0} + \frac{\hat{z}_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(\hat{z}_{0} + z_{1 - \alpha/2})}\right).
\end{equation*}
A $(1 - \alpha)100\%$ ~BCA CI is
\[
(\hat\theta_{n, \alpha_1}^{B}, \quad \hat\theta_{n, \alpha_2}^{B}).
\]
This CI is not necessarily centered by $\hat\theta_n$. The BCA method corrects 
for bias and skewness of the $B$ bootstrap point estimates 
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including 
bias-correction and acceleration factors. The acceleration factor refers to the 
rate of change of the standard error of $\hat\theta_n$ with respect to $\theta$.

@@

\jy{I like the font size of the labels and axis of Figure 4. They are still
  overly large in Figures 1--3. The panel head is also too wide. The axis ticks
  look crowded. The panel
  labels on the right also does not look pretty. I'd prefer the old version if
  the font sizes were smaller.}
\mc{addressed}

@@

\jy{Is textbf of Figure requried? Never manual formatting.}
\mc{The guide says "When you need to refer to Figure 1, Reference 1, Table 1, 
Scheme 1, Step 1, and Equation 1 please bold those words in the text (size 10) 
and in the title (size eight)." If I don't use textbf, the references don't get
bolded by default.}
For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu}} suggests 
that all methods eventually approach correct coverage of $\mu$ as sample size 
increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
correct coverage, except for samples with strong negative dependence, in which 
case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
nominal level for all combinations of $n$ and $\phi$. All methods seem to 
require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
negative dependence versus positive dependence. For example, BC CIs recover 
$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
stronger, holding everything else equal, coverage increases, which lead to the 
Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
stronger, holding everything else equal, coverage decreases, and a larger sample 
is necessary to recover~$\mu$.

@@

To calibrate the copula parameters, we first constructed a multivariate
exponential distribution from a normal copula using the \textsl{copula} package.
\citep{nelsen2006introduction} Then we computed $E[XY]$, which 
requires double integration using the \textsl{pracma} package. \citep{pracma} 
Finally, we obtained true $\rho = E[XY] - 1$, which was used as the target
parameter when evaluating CI performance when estimating $\rho$.
After this step, we again plotted empirical coverage 
rates for $\mu$, $\sigma$, and $\rho$, as well as 95\% confidence intervals of 
the real coverage. These are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_rho}}.

@@

\jy{cite the copula book instead of the package} \mc{i cited the nelsen book 
referenced in the manual}

\jy{comment on the similarity of the results with those reported in the main 
text.} \mc{addressed}

@@

Iit seems that range of sample sizes needed 
to cover parameters of an exponentially distributed AR(1) process is generally 
higher than that needed to cover parameters of a normally.
distributed AR(1) process. Despite this, the trends and patterns discussed 
previously with respect
to the performance of different methods and with different parameters are the 
same.
For instance, Student's $t$ CIs still appear to yield higher coverage rates than 
other 
methods. Performance is still generally better when temporal dependence is 
negative rather than positive. Most importantly, percentile, BC, and BCA CIs
still deteriorate in coverage of $\rho$ as sample size increases. As exhibited 
in Figure~\ref{fig:eri}, percentile and BC CIs still have the same bias
issue. Overall, the results with an underlying marginal exponential distribution 
are very similar to the results with an underlying normal distribution from the
main study.
